New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-06 Manuscript/Manuscript.Rmd
Interaction strength estimation

See the defaults and examples from the skeleton and the official
Copernicus documentation for details.

@@

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012. The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions. GATEWAy v.1.0 does provide information on the mean mass for consumers and resources for every interaction, but lacks the dimensionality for 924 interactions. To solve this issue, we used the information about movement type for consumer and resource. Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource). The interaction was classified as 3D when both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].

The main equation for estimating the interaction strength IS is [@Pawar2012]:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively. We obtained the search rate and the resource density from the relationship with the consumer and resource mass, respectively, suggested by @Pawar2012. Such relationship, a linear regression, varies with the interaction dimensionality.

>>>>

@@

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012. The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions. GATEWAy v.1.0 does provide information on the mean mass for consumers and resources (except for 'detritus' and 'sediment') for every interaction, but lacks the dimensionality for 924 interactions. To solve this issue, we used the information about movement type for consumer and resource. Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource). The interaction was classified as 3D when both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].

The main equation we used for estimating the interaction strength IS is [@Pawar2012]:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively.

We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively (@Pawar2012). The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality. On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy v.1.0, we calculated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012). On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

### 2022-08-06 Manuscript/Manuscript.tex
Interaction strength estimation

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are: body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality classified as 2 or 3
dimensions. GATEWAy v.1.0 does provide information on the mean mass for
consumers and resources for every interaction, but lacks the
dimensionality for 924 interactions. To solve this issue, we used the
information about movement type for consumer and resource. Then, we
classified the interaction as 2D when both consumer and resource move in
2D (e.g., both are sessile or walking) or if a consumer moves in 3D and
a resource in 2D (e.g., swimming consumer and sessile/walking resource).
The interaction was classified as 3D when both consumer and resource
move in 3D (e.g., both swimming) or if the consumer moves in 2D and
resource in 3D (e.g., sessile/walking consumer, swimming resource)
\citep{Pawar2012}.

The main equation for estimating the interaction strength IS is
\citep{Pawar2012}:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
and the consumer, respectively. We obtained the search rate and the
resource density from the relationship with the consumer and resource
mass, respectively, suggested by \citet{Pawar2012}. Such relationship, a
linear regression, varies with the interaction dimensionality.

>>>>

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are: body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality classified as 2 or 3
dimensions. GATEWAy v.1.0 does provide information on the mean mass for
consumers and resources (except for `detritus' and `sediment') for every
interaction, but lacks the dimensionality for 924 interactions. To solve
this issue, we used the information about movement type for consumer and
resource. Then, we classified the interaction as 2D when both consumer
and resource move in 2D (e.g., both are sessile or walking) or if a
consumer moves in 3D and a resource in 2D (e.g., swimming consumer and
sessile/walking resource). The interaction was classified as 3D when
both consumer and resource move in 3D (e.g., both swimming) or if the
consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer,
swimming resource) \citep{Pawar2012}.

The main equation we used for estimating the interaction strength IS is
\citep{Pawar2012}:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
and the consumer, respectively.

We obtained estimations for the resource density and the search rate
from the scaling relationships with the resource and the consumer mass,
respectively (\citet{Pawar2012}). The coefficients of such
relationships, determined by ordinary least squares regression, vary
with the interaction dimensionality. On one hand, resource density
scales with resource mass as a power-law with exponents
\vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since
mean mass for resources `detritus' and `sediment' were not available in
GATEWAy v.1.0, we calculated it considering the scaling relationship
with consumer mass, also different in 2D and 3D (for details see
equation S9 and figures 2c-d of Supplementary Information in
\citet{Pawar2012}). On the other hand, search rate scales with consumer
mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and
\vec{p = 1.05 \pm 0.08} in 3D.
